---
title: "Course Project 2 - Plotly"
subtitle: "Developing Data Products"
author: "Aubin Bannwarth"
date: "14/08/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE,
  warning = FALSE
)
```

## Summary

This is the web presentation created for the second course project in the *Developing Data Products* course by Johns Hopkins University on Coursera.  

The assignment was to create a web presentation using R Markdown, and to include a plot created with **plotly**.  

## Creating the plotly interactive plot - I


We begin by loading the **plotly** and **tidyverse** packages:

```{r}
library(plotly)
library(tidyverse)
```

**tidyverse** includes the **ggplot2** package that will be used in the next slide to create a simple non-interactive plot, before being converted to a **plotly** object using `ggplotly()`.

## Creating the plotly interactive plot - II

We will use the `diamonds` dataset that comes with **ggplot2**. We can create a plot using the usual **ggplot2** syntax and assign the result to a variable `my_ggplot`:
```{r}
my_ggplot <- diamonds %>%
  ggplot() +
  geom_freqpoly(aes(x = price, y = ..density.., color = clarity)) +
  labs(
    title = "Distribution of diamond prices by clarity", 
    x = "Price (USD)",
    y = "Density",
    color = "Clarity"
  )
```
## Creating the plotly interactive plot - III
We now only need to pass our `my_ggplot` object to the `ggplotly()` function:
```{r, fig.width=5, fig.asp=0.618, out.width="70%", fig.align='center'}
my_ggplot %>% ggplotly()
```

